Streaming Fact Extraction for Wikipedia Entities at Web-Scale

### 2014-01-29 paper/flairs27_AuthorKit/paper.tex
Adding authors contributed equally.

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algorithmic} 
\usepackage{cite }
%\usepackage{natbib}

\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Streaming Fact Extraction for Wikipedia Entities at Web-Scale)
/Author (Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang, Milenko Petrovic)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Streaming Fact Extraction for Wikipedia Entities at Web-Scale}
\author{Morteza Shahriari Nia, Christan Grant, \\
\bf \large Yang Peng, Daisy Zhe Wang\\
Data Science Research Lab\\
University of Florida\\\
Gainesville, Florida 32611\\
\And Milenko Petrovic\\
Institute for Human and Machine Cognition\\ 15 SE Osceola Ave \\\ Ocala, Florida 34471
}

@@

Wikipedia.org (WP) is the largest and most popular general reference work on the Internet.
The website is estimated to have nearly 365 million readers worldwide.
An important part of keeping WP usable it to include new and current content.
%An important challenge in maintaining WP, the most popular web-based, collaborative, multilingual KB on the internet, is making sure its contents are up-to-date.
Presently, there is considerable time lag between the publication of an event and its citation in WP\@.
The median time lag for a sample of about 60K web pages cited by
 WP articles in the \textit{living\_people} category is over a year
 and the distribution has a long and heavy tail~
 \cite{frank2013building}.
%Also, the majority of WP entities have updates on their associated article much less frequently than their mention frequency.
Such stale entries are the norm in any large reference work because the number
of humans maintaining the reference is far fewer than the number of entities.

Reducing latency keeps WP relevant and helpful to its users.
Given an entity page, such as \textsl{wiki/Boris\_Berezovsky\_(businessman)}\footnote{http://en.wikipedia.org/wiki/Boris\_Berezovsky\_(businessman)},
possible citations may come from a variety of sources.
Notable news may be derived from newspapers, tweets, blogs and a variety of
different sources include Twitter, Facebook, iBlogs, arxiv, etc.
However, the actual citable information is a small percentage of the total documents that appear on the web.
%We develop a system to read streaming data and filter out articles that are candidates for citations. 
%The goal of this system is to read web documents and recommend citable facts (attributes) for WP pages.
To help WP editors, a system is needed to parse through terabytes of documents 
and select facts that can be recommended to particular WP pages.

Previous approaches are able to find relevant documents given a list of WP
entities as query nodes \cite{mcnamee2012hltcoe}
 \cite{dalton2013bi}\,
\cite{
Bonnefoy:2013:WDE:2484028.2484180, Balog:2013:CCR:2484028.2484151,ji2011knowledge}.
Entities of three categories \textit{person}, \textit{organization} and \textit{facility} are considered.
This work involves processing large sets of information to determine which facts may contain references to a WP entity. 
This problem becomes increasingly more difficult when we look to extract relevant facts from
each document.
Each relevant document must now be parsed and processed to determine if a sentence or paragraph is worth being cited.
% Reorder this paragraph
%The challenges that we address are: first finding documents that contain useful information about the entity (avoid spams, documents that do not have direct information about the entity even though they mention them, etc), the scale where \textit{stream processing} nature of the system makes it suitable to avoid batch processing natures of Hadoop and operate in the realm of streams such as twitter storm~\footnote{http://storm-project.net/} which similarly processes unblounded streams of twitter data or Spark Streaming~\footnote{http://spark.incubator.apache.org/}. Further, this is called streaming because data is being generated as time goes
%on and for each extraction we should only consider current or past data. As other Natural Language Processing tasks, precision and recall of the extent we can extract slot values are very important metrics that we will discuss later on. Having to balance between infamous and obscure entities, dealing with slots that can be very broad (e.g.\ things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).

@@

\bibliography{citation}
\bibliographystyle{aaai}

>>>>

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algorithmic} 
%\usepackage{cite }
%\usepackage{natbib}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Streaming Fact Extraction for Wikipedia Entities at Web-Scale)
/Author (Morteza Shahriari Nia, Christan Grant, Yang Peng, Daisy Zhe Wang, Milenko Petrovic)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Streaming Fact Extraction for Wikipedia Entities at Web-Scale}
\author{Morteza Shahriari Nia$*$, Christan Grant$*$, \\
\bf \large Yang Peng\footnote{All authors contributed equally.}, Daisy Zhe Wang\\
Data Science Research Lab\\
University of Florida\\\
Gainesville, Florida 32611\\
\And Milenko Petrovic\\
Institute for Human and Machine Cognition\\ 15 SE Osceola Ave \\\ Ocala, Florida 34471
}

@@

Wikipedia.org (WP) is the largest and most popular general reference work on the Internet.
The website is estimated to have nearly 365 million readers worldwide.
An important part of keeping WP usable it to include new and current content.
%An important challenge in maintaining WP, the most popular web-based, collaborative, multilingual KB on the internet, is making sure its contents are up-to-date.
Presently, there is considerable time lag between the publication of an event and its citation in WP\@.
The median time lag for a sample of about 60K web pages cited by
 WP articles in the \textit{living\_people} category is over a year
 and the distribution has a long and heavy tail
 \cite{frank2013building}.
%Also, the majority of WP entities have updates on their associated article much less frequently than their mention frequency.
Such stale entries are the norm in any large reference work because the number
of humans maintaining the reference is far fewer than the number of entities.

Reducing latency keeps WP relevant and helpful to its users.
Given an entity page, such as \textsl{wiki/Boris\_Berezovsky\_(businessman)}\footnote{http://en.wikipedia.org/wiki/Boris\_Berezovsky\_(businessman)},
possible citations may come from a variety of sources.
Notable news may be derived from newspapers, tweets, blogs and a variety of
different sources include Twitter, Facebook, Blogs, arxiv, etc.
However, the actual citable information is a small percentage of the total documents that appear on the web.
%We develop a system to read streaming data and filter out articles that are candidates for citations. 
%The goal of this system is to read web documents and recommend citable facts (attributes) for WP pages.
To help WP editors, a system is needed to parse through terabytes of documents 
and select facts that can be recommended to particular WP pages.

Previous approaches are able to find relevant documents given a list of WP
entities as query nodes \cite{mcnamee2012hltcoe}
 \cite{dalton2013bi}\,
\cite{Bonnefoy:2013:WDE:2484028.2484180, Balog:2013:CCR:2484028.2484151,ji2011knowledge}.
Entities of three categories \textit{person}, \textit{organization} and \textit{facility} are considered.
This work involves processing large sets of information to determine which facts may contain references to a WP entity. 
This problem becomes increasingly more difficult when we look to extract relevant facts from
each document.
Each relevant document must now be parsed and processed to determine if a sentence or paragraph is worth being cited.
% Reorder this paragraph
%The challenges that we address are: first finding documents that contain useful information about the entity (avoid spams, documents that do not have direct information about the entity even though they mention them, etc), the scale where \textit{stream processing} nature of the system makes it suitable to avoid batch processing natures of Hadoop and operate in the realm of streams such as twitter storm~\footnote{http://storm-project.net/} which similarly processes unblounded streams of twitter data or Spark Streaming~\footnote{http://spark.incubator.apache.org/}. Further, this is called streaming because data is being generated as time goes
%on and for each extraction we should only consider current or past data. As other Natural Language Processing tasks, precision and recall of the extent we can extract slot values are very important metrics that we will discuss later on. Having to balance between infamous and obscure entities, dealing with slots that can be very broad (e.g.\ things that an entity is affiliated with) or very specific (such as cause of death of a \textit{person} entity).

@@

\bibliographystyle{aaai}

\bibliography{citation}
